Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
SDSS acronym, reference

To achieve this empirical calibration, we must adopt a set of calibrator
objects for which true optical reddening is known. There are various 
possibilities at our disposal. \cite{planckdust} calibrated their single MBB
$\tau_{353}$ to $E(B-V)$ using broadband SDSS photometry for a set of 
$\sim$10$^5$ quasars. The SFD calibration was originally tied to a few
hundred elliptical galaxies, but was later revised by \cite{schlafly10} using 
several hundred thousand stars with both spectroscopy and broadband photometry 
available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
the same set of stars studied by \cite{schlafly10}.

>>>>

To achieve this empirical calibration, we must adopt a set of calibrator
objects for which true optical reddening is known. There are various 
possibilities at our disposal. \cite{planckdust} calibrated their $\tau_{353}$ 
to $E(B-V)$ using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} 
photometry for a set of $\sim$10$^5$ quasars. The SFD calibration was 
originally tied to a few hundred elliptical galaxies, but was later revised by 
\cite{schlafly10} using several hundred thousand stars with both spectroscopy 
and broadband photometry available from SDSS. To calibrate our $\tau_{545}$ to 
reddening, we make use of the same set of stars studied by \cite{schlafly10}.
